### 2024-09-27 uw-ethesis-frontpgs.tex
small changes to intro
new

        Waterloo, Ontario, Canada, 2022 \\

@@

        \copyright\ Xintong Li, 2022 \\
        \end{center}
\end{titlepage}

@@

Quantitative risk management of modern financial derivatives and actuarial products is intricate and often requires modelling the underlying stochasticity with Monte Carlo simulations.
A simulation scheme is flexible, and it can easily adapt to changes in model assumptions and market conditions.
However, as multiple sources of risk are considered for long time horizons, such simulation schemes become expensive to implement. 
Tremendous research effort is dedicated in the design of computationally efficient machine learning-based procedures that mitigate the computational burden of a standard simulation procedure.
In machine learning, model flexibility comes at the expense of model resilience, which is especially crucial for risk management tasks.
This study considers the management of tail risk for complex financial and actuarial products with resilient machine learning-based nested simulation procedures and reinforcement learning-based hedging policies.
Our approaches offer significant improvements over a standard simulation procedures and illustrate a resilient machine learning model is built by accounting for problem complexity and data structure, quality, and quantity.

>>>>

        Waterloo, Ontario, Canada, 2024 \\

@@

        \copyright\ Xintong Li, 2024 \\
        \end{center}
\end{titlepage}

@@

Quantitative risk management of modern financial derivatives and actuarial products is intricate and often requires modelling the underlying stochasticity with Monte Carlo simulations.
A simulation scheme is flexible, and it can easily adapt to changes in model assumptions and market conditions.
However, as multiple sources of risk are considered for long time horizons, such simulation schemes become expensive to implement. 
Tremendous research effort is dedicated in the design of computationally efficient machine learning-based procedures that mitigate the computational burden of a standard simulation procedure.
In machine learning, model flexibility comes at the expense of model resilience, which is especially crucial for risk management tasks.
This study considers the management of tail risk for complex financial and actuarial products with resilient machine learning-based nested simulation procedures.
We propose a novel metamodeling approach that integrates deep neural networks within the nested simulation framework for efficient risk estimation.
Our approaches offer significant improvements over a standard simulation procedures and illustrate a resilient machine learning model is built by accounting for problem complexity and data structure, quality, and quantity.
To further enhance adaptability to new VA contracts and changing market conditions, the thesis introduces transfer learning techniques. 
By reusing and fine-tuning pre-trained metamodels, the approach accelerates the adaptation process to different contract features and evolving market dynamics without the need for retraining models from scratch. 
Transfer learning improves computational efficiency ando enhances the robustness and flexibility neural network metamodels in dynamic hedging of variable annuities.

Extensive numerical experiments demonstrate that the proposed method achieves substantial improvements in computational efficiency, reducing simulation times by orders of magnitude compared to standard nested simulation procedures.
The results indicate that the deep neural network metamodels with transfer learning can quickly adapt to new market scenarios and contract specifications.
The findings of this research contribute to the advancement of risk management practices for complex actuarial products and financial derivatives.
By leveraging advanced machine learning techniques, the thesis offers a practical and scalable solution for insurers to perform timely and accurate risk assessments.
The integration of LSTM metamodels and transfer learning into the nested simulation framework represents a significant step toward more efficient, adaptable, and robust methodologies in actuarial science and quantitative finance.
